%------------------------
% Resume Template - Corrected for TeXShop
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,12pt]{article} % Corrected: 20pt is not a standard article font size. Changed to 12pt.

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor} % Use xcolor for more flexibility
\usepackage{verbatim}
\usepackage{enumitem} 
\usepackage{fancyhdr}
\usepackage[colorlinks,urlcolor=blue]{hyperref} % Corrected: Single, clean hyperref call.

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Yang Yang}\\
  Email: \href{mailto:yang.yang@insight-centre.org}{yang.yang@insight-centre.org}\\
  Website: \href{https://yang233666.github.io/}{https://yang233666.github.io/}\\
  Location: Lower Dangan, Galway, H91 AEX4, Ireland.\\
\end{tabular*}

%-----------Research Interests-----------------
\section{Research Interests}
\begin{itemize}
\item {Knowledge Graphs, Trustworthy AI, Large Language Models, Agents.}
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}
\begin{itemize}
\item {September 2023 - Now: PhD student in Insight Research Ireland Centre for Data Analytics, Data Science Institute, University of Galway (Advisor: \href{https://edwardcurry.org}{Edward Curry}).}
\item {June 2024: International Semantic Web Research Summer School (ISWS), Bertinoro, Italy.}
\item {September 2019 - June 2022: M.E. in Nankai University (Advisor: \href{https://scholar.google.com/citations?user=Q_U6r_YAAAAJ&hl=en}{Wei Shen}).}
\item {September 2015 - June 2019: B.E. in Dalian University of Technology. }
\end{itemize}

\section{Publications}
\begin{itemize}
\item {\textbf{Yang Yang}, Mohan Timilsina, Edward Curry. “\href{}{KGE Calibrator: An Efficient Probability Calibration Method of Knowledge Graph Embedding Models for Trustworthy Link Prediction}” In EMNLP 2025. }

\item {\textbf{Yang Yang}, Edward Curry. “\href{https://ebooks.iospress.nl/volumearticle/72299}{Neuro-Symbolic Techniques in Open Knowledge Graph Canonicalization}” In Handbook on Neurosymbolic AI and Knowledge Graphs 2025. }

\item {\textbf{Yang Yang}, Wei Shen, Junfeng Shu, Yinan Liu, Edward Curry, Guoliang Li. “\href{https://drive.google.com/file/d/19y55BQx21IJrOf-jqywshk4yBrQE0ANr/view}{CMVC+: a Multi-View Clustering Framework for Open Knowledge Base Canonicalization via Contrastive Learning}” In IEEE TKDE 2025. }

\item {\textbf{Yang Yang}, Edward Curry. “\href{https://ceur-ws.org/Vol-3747/text2kg_paper5.pdf}{Open Knowledge Base Canonicalization: Techniques and Challenges}” In TEXT2KG Workshop at ESWC 2024. }

\item {Wei Shen, \textbf{Yang Yang}$^{*}$, Yinan Liu. “\href{https://dl.acm.org/doi/abs/10.1145/3534678.3539449}{Multi-View Clustering for Open Knowledge Base Canonicalization}” In KDD 2022 ($^{*}$Corresponding author). }

\item {Wei Shen, Yuwei Yin, \textbf{Yang Yang}, Jiawei Han, Jianyong Wang, Xiaojie Yuan. “\href{https://drive.google.com/file/d/1OXgXAR6FQsnNHFkYkdKYR9XvXrhDcDja/view}{Toward Tweet Entity Linking with Heterogeneous Information Networks}.” In IEEE TKDE 2021. }

\item {Edward Curry, Tarek Zaarour, \textbf{Yang Yang}, Mohan Timilsina, Majjed Al-Qatf, Rafiqul Haque. “\href{https://drive.google.com/file/d/1tg188Hmcf2UZfPNU85NgRhaFfhiK_vg5/view}{Foundation Data Space Models: Bridging the Artificial Intelligence and Data Ecosystems (Vision Paper).}” In IEEE BigData 2023. }

\item {Mohan Timilsina, Samuele Buosi, Ping Song, \textbf{Yang Yang}, Rafiqul Haque, Edward Curry. “\href{https://drive.google.com/file/d/1pHXlfak9GEc0Z5LBGY3x7HvKhlbvSFla/view}{Enabling Dataspaces Using Foundation Models: Technical, Legal and Ethical Considerations and Future Trends.}” In IEEE BigData 2023. }
\end{itemize}

%-----------Awards-----------------
%\section{Honors and Awards}
%\begin{itemize}
%\item {Outstanding Graduates Award, Dalian University of Technology - June, 2019}
%\vspace{-5pt}
%\item {Merit Student Award, Dalian University of Technology - December, 2017}
%\vspace{-5pt}
%\item {Learning Excellence Award, Dalian University of Technology - October, 2017}
%\vspace{-5pt}
%\item {Merit Student Award, Dalian University of Technology - December, 2016}
%\vspace{-5pt}
%\item {Learning Excellence Award, Dalian University of Technology - October, 2016}
%\vspace{-5pt}
%\end{itemize}

\vspace{-5pt}
\section{Teaching Experience}
I work as a teaching assistant mainly servicing for the following courses:
\vspace{-5pt}
\begin{itemize}
\item {C++ Programming (2-2), March 2021 - July 2021, Nankai University}
\vspace{-5pt}
\item {C++ Programming (2-1), October 2020 - January 2021, Nankai University}
\end{itemize}


\vspace{-5pt}
\section{Language}
\begin{itemize}
\item {Chinese Mandarin (Native)}
\vspace{-5pt}
\item {English (Fluent)}
\end{itemize}

\vspace{-5pt}
\section{Skills}
\begin{itemize}
\item {Programming: Python, C++, Java, Git}
\vspace{-5pt}
\item {Frameworks: Pytorch, Tensorflow, Keras.}
\vspace{-5pt}
\item {Others: Microsoft Office, Latex}
\end{itemize}

\end{document}